Long name of the paper

### 2018-10-29 anzjs2018/sections/04_implementation.tex
words

Figure~\ref{fig:timings} shows the timing results for varying number of particles.
As expected,

Nothing too exciting going on here, 
except that writing ETAs takes up the largest chunk of time,
as this involves calculating quantiles which require the estimated ETAs to be sorted,
which is computationally demanding. 
The vehicle update takes the second longest time,
and involves copying particles during the update resampling step.
Finally, predicting the ETAs is pretty quick.
The remaining parts of the application take negligible time,
and all run on a single core to avoid mutex locks.

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{figures/04_model_results_timing.pdf}
    \caption{The timings for various parts of the application, and overall. %
        The trend is approximately linear with the number of particles.}
    \label{fig:timings}
\end{figure}

>>>>

Figure~\ref{fig:timings} shows the timing results for varying number of particles.
We see that there is a very slight quadratic trend to run times,
as several steps are not of complexity $O(N)$,
the main one being the estimation of ETA quantiles.
While not discussed in this paper,
the application generates ETAs for each particle
and calculates ETA quantiles for each vehicle to demonstrate the computational faesibility.
This step requires sorting a vector, which is $O(N\log(N))$.
Clearly, our initial target of 30~seconds is obtainable given the number of particles
is not too large, and there are enough cores.

\begin{figure}[tb]
    \centering
    \includegraphics[width=0.7\textwidth]{figures/04_model_results_timing.pdf}
    \caption{The timings for various parts of the application, and overall. %
        The trend is slightly non-linear due to the complexity of the ETA generation step, %
        which requires sorting of the particle ETAs to obtain quantile estimates.}
    \label{fig:timings}
\end{figure}
